Alleviating Topology Mismatch in Distributed Overlay Networks: A Survey

### 2014-01-27 structured.tex
2012.11.19 (Hüseyin) Resolving similarity issues.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LAPTOP}
\emph{LAPTOP} \cite{WLH2007}, organizes the overlay into a tree-based hierarchy
with main focus on reducing hops during message routing as well as minimizing
maintenance overhead. Additionally, a caching scheme is also incorporated so as
to further reduce routing table update costs. The authors theoretically show
that in LAPTOP routing path length is bounded by $O(log_d N)$ and node joining
and leaving in the overlay network is bounded by $O\left( d log_d N \right)$
hops in a balanced overlay tree, where $N$ is the number of nodes, and $d$ is
the maximum degree of each node. LAPTOP implements the geographical layout
approach  and constructs its layout in a self-organizing and efficient fashion,
by estimating the round-trip times to a small number of nodes in the overlay
network in order to make them roughly aware of their physical distances among
them.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{T2MC}
T2MC \cite{SLCGZ2008} uses trace-route logs to detect different autonomous
systems and cluster close by peers, thus reducing redundant traffic that crosses
autonomous system boundaries. T2MC uses a customized k-mean classification
algorithm with $k=2$ to perform the classification, and exploits the stable
structure of the Internet routers to guide clustering. The peer chooses the
minimum and maximum Latency results from the trace-route to initialize the
centroids of two sets. Then the peer calculates, for all hops along its
trace-routed path, the peer calculates the absolute distance to these centroids
of both sets and assigns the routers to that centroid with which it has the
smaller absolute distance. After that, the mean and variance values are
calculated and if the variance is larger than a predefined threshold then the
algorithm sets the two latency mean values as new centroids for the two sets and
loops again. Ultimately peer will end up with two sets having the minimum
intra-set variance. The peer, then, chooses the router from the second set with
the minimum hops attribute and sets it as a threshold. The selected router and
all others whose hops attribute is larger than the threshold are classified as
\emph{remote} router cluster. The remaining are classified as \emph{near}. From
the near class, the peer chooses the one with maximum hops attribute as its edge
router, and registers it along with all near clusters into the DHT of the
P2P overlay. As new peers join the network, those that share the same edge
router or any of the members of the near router clusters, would form a close
peer cluster. As Edge routers can provide more valuable information than other
members of the near set, T2MC was designed to prioritize interaction of peers
and edge gateways.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LAPTOP}
\emph{LAPTOP} \cite{WLH2007}, organizes the overlay into a tree-based hierarchy
with main focus on reducing hops during message routing as well as minimizing
maintenance overhead. Additionally, a caching scheme is also incorporated so as
to further reduce routing table update costs. The authors theoretically show
that in LAPTOP routing path length is bounded by $O(log_d N)$ and node joining
and leaving in the overlay network is bounded by $O\left( d log_d N \right)$
hops in a balanced overlay tree, where $N$ is the number of nodes, and $d$ is
the maximum degree of each node. LAPTOP implements the geographical layout
approach  and constructs its layout in a self-organizing and efficient fashion.
The physical distances are estimated with round trip times to a few existing
nodes in the overlay network.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{T2MC}

T2MC \cite{SLCGZ2008} uses traceroute logs to detect the AS boundaries and
cluster close by peers with each other to reduce the redundant multiple message
passes between the AS boundaries. T2MC uses a customized k-mean classification
algorithm with k = 2 to perform the classification, and exploits the stable
structure of the internet routers to guide clustering. Even though traceroute
provides detailed information about the network structure, use of traceroute
creates overhead to the overall network structure. For this same reason, it is
not unusual for network administrators to disable this support on their network
routers, which may affect the performance of the T2MC algorithm.

%T2MC \cite{SLCGZ2008} uses trace-route logs to detect different autonomous
%systems and cluster close by peers, thus reducing redundant traffic that crosses
%autonomous system boundaries. T2MC uses a customized k-mean classification
%algorithm with $k=2$ to perform the classification, and exploits the stable
%structure of the Internet routers to guide clustering. The peer chooses the
%minimum and maximum Latency results from the trace-route to initialize the
%centroids of two sets. Then the peer calculates, for all hops along its
%trace-routed path, the peer calculates the absolute distance to these centroids
%of both sets and assigns the routers to that centroid with which it has the
%smaller absolute distance. After that, the mean and variance values are
%calculated and if the variance is larger than a predefined threshold then the
%algorithm sets the two latency mean values as new centroids for the two sets and
%loops again. Ultimately peer will end up with two sets having the minimum
%intra-set variance. The peer, then, chooses the router from the second set with
%the minimum hops attribute and sets it as a threshold. The selected router and
%all others whose hops attribute is larger than the threshold are classified as
%\emph{remote} router cluster. The remaining are classified as \emph{near}. From
%the near class, the peer chooses the one with maximum hops attribute as its edge
%router, and registers it along with all near clusters into the DHT of the
%P2P overlay. As new peers join the network, those that share the same edge
%router or any of the members of the near router clusters, would form a close
%peer cluster. As Edge routers can provide more valuable information than other
%members of the near set, T2MC was designed to prioritize interaction of peers
%and edge gateways.

### 2014-01-27 unstructured.tex
2012.11.19 (Hüseyin) Resolving similarity issues.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Overlay Topology Optimization (AOTO)}
\emph{Adaptive Overlay Topology Optimization (AOTO)} \cite{LZXN2003} is one
of the first attempts, along with Narada, to address the topology mismatch
problem. AOTO is a distributed algorithm that works in two steps, namely
\emph{Selective Flooding} and \emph{Active Topology} to optimize the usage of
the underlying physical resources. In \emph{Selective Flooding} a minimum
spanning tree is built among each peer and its immediate neighbors so that
queries are not flooding the whole network and at the same time without
shrinking the search scope. During \emph{Active Topology}, the overlay
links are revised so that they depict the physical network topology as close as
possible. This is done independently, by each peer by replacing non-flooding
neighbors, with closer nodes. Picking a replacement out of these non-flooding
neighbors follows a random policy (called \emph{Randomized AT} algorithm in the
paper's context). For these steps a peer needs to keep track of communication
costs to all its neighbors (e.g. the network delay) as well as between any
pair of neighbors (meaning also that additional, cost probing, message types
need to be added to the Gnutella protocol). Whenever a new neighbor cost table
is received or there is a change of neighbors, the source peer has to
re-calculate the multi-cast tree and apply the randomized AT algorithm.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Connection Establishment (ACE)}
\emph{Adaptive Connection Establishment (ACE)} \cite{LZXN2004} builds an
overlay multi-cast tree among each source node and the peers within a certain
diameter from the source peer and optimizes the neighbor connections that are
not in that tree. To achieve that, it calculates cost between nodes using
network delay as a metric. Each peer probes the costs with its immediate logical
neighbors and forms a \emph{neighbor cost table (NCT)} using a special
routing message type. Two neighboring peers exchange their NCTs in order for
every peer to obtain the cost between any pair of its local neighbors forming a
small overlay topology. Moreover, based on obtained NCTs a minimum spanning tree
among each peer and its immediate neighbors is built. Ultimately, physically
far away neighbors are replaced by physically close ones. Specifically, a peer
$S$ probes the distance between one of its non-flooding neighbor's neighbor,
say $G$ and $H$ respectively. Assuming that the neighbor's neighbor ($SH$) is
measured as being ``closer'' that the neighbor ($SG$), the link to the later
is cut and a new connection is established. In the opposite situation where
distance $SG$ is closer than $SH$ then if $SH$ is shorter that $GH$ then $H$ is
preserved as $S$'s new neighbor. In the case where $SH$ is larger than $SG$ and
$GH$, no connection will be established and $S$ will continue probing another
neighbor's neighbor. The above optimization is conducted within $1$-neighbor
closure (among its source peer and all its direct neighbors) but the scope can
be extended. The larger the scope, the better topology matching improvement but
also the greater the computational overhead.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Two-Hop-Away Neighbor Comparison and Selection (THANCS)}
Work in \cite{LNXE2005,L2008} proposes a distributed heuristic
called \emph{Two-Hop-Away Neighbor Comparison and Selection (THANCS)} that
tries to minimize the overlay hop costs. THANCS is considered a \emph{local
search method}, in the sense that it targets in finding a locally optimum
solution, by exploiting knowledge within a 2-hop radius. The algorithm consists
of two main components: \emph{piggybacking neighbor distance on queries} and
\emph{neighbor comparison and selection} which are further discussed bellow.
The first component dictates peers to probe distances (using network delay
distance measuring) with its immediate neighbors and stores information
locally. This is done by introducing a special query message type, the
\emph{Piggy Message (PM)} which includes information about the neighbor
identification and measured distance. A peer $p$ constructs a PM for its
neighbor $n$, which contains $n$'s IP address and the distance between them.
When $p$ receives a query from $n$, this PM will be piggybacked to the query
message that will be then forwarded to all other neighbors of peer $p$. Upon
receiving such a query message, each of the other neighbors will detach the PM
information (it will not be further forwarded), record the $pq$ distance and
process the query as always. Selection of which incoming queries should
piggyback a PM is proposed by either \emph{pure probability-based (PPB)} or
\emph{new neighbor triggered (NNT)} policies. The second component, namely
neighbor comparison and selection, dictates peer $p$ to probe the distance to
all his known, not yet probed, two-hop neighbors ($ N^2(p)$). The distance of
$pn$ is known to $p$. Upon receiving a PM from node $n$ with the distance of
$nq$, where $q$ is a direct neighbor of $n$, $p$ chooses one of the following
two paths. First, if $q$ is a direct neighbor of $p$, then the later will check
the cost of the involved links. If the most cost-intensive link is one of $pq$
or $pn$, then it is put into a \emph{will-cut} list. If it is $nq$ then nothing
is done (since either $n$ or $q$ will have the chance to handle it themselves).
On the other hand, if $q$ is within two-hop radius from $p$, the later probes
the former (if it hasn't got the distance information yet) and again compares
distances $pq$, $pn$ and $nq$. If $pq$ is the most cost-intensive, $p$ will not
establish the connection. If it is $pn$, $p$ will establish connection $pq$ and
put $pn$ in the will-cut list. If it is $nq$, $p$ will keep the connection with
both $n$ and $q$, expecting that eventually either $n$ or $q$ will disconnect
link $nq$, later.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Hops Adaptive Neighbor Discovery (HAND)}
\cite{CLZHC2006} proposes the \emph{HAND} algorithm which uses a
fully distributed triple hop adjustment strategy to address the topology
mismatch problem. The approach's ultimate goal is to shape the current overlay
graph $G$ into the \emph{Logical Communication Network (LCN)} $G^{*}$ which is
how the optimal overlay is referred in the paper's context. A formal
definition of achieving the above match is only if all peer hop sequences $(v_1,
v_2, \ldots, v_k)$ in $G$ exist in $G^{*}$ and in the same order\footnote{In
practice triple sequences $(v_1, v_2, v_3)$ are used.}. The mismatching
detection is done in the following way. Suppose we want to verify peer a
sequence, say $v_2-v_1-v_3$. A pair of probing messages are sent from $v_1$ to
$v_2$ and $v_3$. Suppose delays of $(v_1,v_2)$ and $(v_1,v_3)$ are denoted as
$x$ and $z$, respectively. When the probing message arrives to $v_2$ it forwards
it directly to $v_3$. Similarly, when the probing message arrives to $v_3$, it
forwards it directly to $v_2$. These last steps are performed in order to obtain
delays of $(v_2,v_3)$ and $(v_3,v_2)$ physical paths, respectively, denoted by
$y$. If $y=z-x\pm\varepsilon$, sequence $v_2-v_1-v_3$ is mismatched and should
be adjusted to $v_1-v_2-v_3$ by deleting edge $(v_1,v_3)$ and adding a new
$(v_2,v_3)$. If $y=x-z\pm\varepsilon$, sequence $v_2-v_1-v_3$ is mismatched and
should be adjusted to $v_1-v_3-v_2$ by deleting edge $(v_1,v_2)$ and adding a
new $(v_3,v_2)$, where $\varepsilon$ is a small positive real number denoting
additional delays caused by possible forwarding and jitter delays. The
advantages of the HAND algorithm compared to other approaches are that:
\begin{inparaenum}[\itshape i\upshape)]
  \item it does not need any clock synchronization,
  \item it is a fully distributed algorithm making it robust and reliable in
        decentralized systems,
  \item the traffic overhead of the triple hop adjustment is very low,
  \item it is applicable to dynamic peer-to-peer environments, and
  \item maintains lower query response times.
\end{inparaenum}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Ono}
Choffnes and Bustamante propose Ono \cite{CB2008}, a protocol for managing
BitTorrent traffic so that it significantly reduces cross-ISP traffic and in
the same time enhances downloading rates by favoring connections within the
borders of a single autonomous system. Contrary to biased peer selection
proposed in \cite{BCCMSBZ2006}, this work can lead to improved performance with
no cooperation between ISPs and their subscribers, no additional infrastructure
and no network topology information. The selection approach is landmark-based
and leverages existing CDN infrastructure for peer distance estimation. CDNs
already use both static (i.e. geographical) and dynamic (network measurement
systems) information for their replica selection, so the authors claim that
peers which exhibit similar redirection behavior, are very likely they are close
to the replica servers and as a consequence to each other. The redirection
behavior is modeled in terms of \emph{ratio map} in the article's parlance, a
vector of <replica-server,ratio> tuples, where ratio is the percentage of times
CDN redirects the peer to the specific replica-server. The bootstrapping phase
consists of the peer performing DNS lookup to CDN names in order to build its
redirection information. The interval for polling DNSs starts from 30 seconds
and increases by one minute every time redirection information to the CDN is
found to remain unchanged after a lookup. On the other hand, the interval is
halved whenever is found to have been changed. In order not to avoid the
bootstrapping phase if the ratio map is sufficiently fresh, the protocol
persists the information after the end of a BitTorrent session.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Overlay Topology Optimization (AOTO)}
\emph{Adaptive Overlay Topology Optimization (AOTO)} \cite{LZXN2003} is one
of the first attempts, along with Narada, to address the topology mismatch
problem. AOTO is a distributed algorithm that works in two steps, namely
\emph{Selective Flooding} and \emph{Active Topology} to optimize the usage of
the underlying physical resources. In \emph{Selective Flooding} a minimum
spanning tree is built among each peer and its immediate neighbors so that
queries are not flooding the whole network and at the same time without
shrinking the search scope. During \emph{Active Topology}, the overlay
links are revised so that they depict the physical network topology as close as
possible. This is done independently, by each peer by replacing non-flooding
neighbors, with closer nodes. Picking a replacement out of these non-flooding
neighbors follows a random policy (called \emph{Randomized AT} algorithm in the
paper's context). For these steps a peer needs to keep track of communication
costs to all its neighbors (e.g. the network delay) as well as between any
pair of neighbors (meaning also that additional, cost probing, message types
need to be added to the Gnutella protocol). The randomized AT algorithm is
applied by the source peer everytime the neighbour list is updated or an updated
neighbour cost table is received.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Connection Establishment (ACE)}
\emph{Adaptive Connection Establishment (ACE)} \cite{LZXN2004} uses the network
delay as a metric to calculate the costs between nodes in a spanning tree.
Each peer calculates the costs to its logical one-hop
neighbors and forms a \emph{neighbor cost table (NCT)} using a special
routing message type. Two neighboring peers exchange their NCTs in order for
every peer to obtain the cost between any pair of its local neighbors forming a
small overlay topology. Moreover, based on obtained NCTs a minimum spanning tree
among each peer and its one-hop neighbors is built. Ultimately, physically
far away neighbors are replaced by physically close ones. Specifically, a peer
$S$ probes the distance between one of its non-flooding neighbor's neighbor,
say $G$ and $H$ respectively. Assuming that the neighbor's neighbor ($SH$) is
measured as being ``closer'' that the neighbor ($SG$), the link to the later
is cut and a new connection is established. In the opposite situation where
distance $SG$ is closer than $SH$ then if $SH$ is shorter that $GH$ then $H$ is
preserved as $S$'s new neighbor. In the case where $SH$ is larger than $SG$ and
$GH$, no connection will be established and $S$ will continue probing another
neighbor's neighbor. The above optimization is conducted within $1$-neighbor
closure (among its source peer and all its direct neighbors) but the scope can
be extended. The larger the scope, the better topology matching improvement but
also the greater the computational overhead.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Two-Hop-Away Neighbor Comparison and Selection (THANCS)}
Work in \cite{LNXE2005,L2008} proposes a distributed heuristic
called \emph{Two-Hop-Away Neighbor Comparison and Selection (THANCS)} that
tries to minimize the overlay hop costs. THANCS is considered a \emph{local
search method}, in the sense that it targets in finding a locally optimum
solution, by exploiting knowledge within a 2-hop radius. The algorithm consists
of two main components: \emph{piggybacking neighbor distance on queries} and
\emph{neighbor comparison and selection} which are further discussed bellow.
The first component dictates peers to probe distances (using network delay
distance measuring) with its immediate neighbors and stores information
locally. This is done by introducing a special query message type, the
\emph{Piggy Message (PM)} which includes information about the neighbor
identification and measured distance. A peer $p$ constructs a PM for its
neighbor $n$, which contains $n$'s IP address and the distance between them.
When $p$ receives a query from $n$, this PM will be piggybacked to the query
message that will be then forwarded to all other neighbors of peer $p$. 
Each neighbor will detach the PM information (it will not be further forwarded),
record the $pq$ distance and process the query as always after receiving a query
message. Selection of which incoming queries should piggyback a PM is proposed
by either \emph{pure probability-based (PPB)} or \emph{new neighbor triggered
(NNT)} policies. The second component, namely neighbor comparison and selection,
dictates peer $p$ to probe the distance to all his known, not yet probed,
two-hop neighbors ($ N^2(p)$). The distance of $pn$ is known to $p$. Upon
receiving a PM from node $n$ with the distance of $nq$, where $q$ is a direct
neighbor of $n$, $p$ chooses one of the following two paths. First, if $q$ is a
direct neighbor of $p$, then the later will check the cost of the involved
links. If the most cost-intensive link is one of $pq$ or $pn$, then it is put
into a \emph{will-cut} list. If it is $nq$ then nothing is done (since either
$n$ or $q$ will have the chance to handle it themselves).  On the other hand, if
$q$ is within two-hop radius from $p$, the later probes the former (if it hasn't
got the distance information yet) and again compares distances $pq$, $pn$ and
$nq$. If $pq$ is the most cost-intensive, $p$ will not establish the connection.
If it is $pn$, $p$ will establish connection $pq$ and put $pn$ in the will-cut
list. If it is $nq$, $p$ will stay connected with both $n$ and $q$,
such that eventually in later stages either $n$ or $q$ will disconnect link $nq$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Hops Adaptive Neighbor Discovery (HAND)}
\cite{CLZHC2006} proposes the \emph{HAND} algorithm which uses a
fully distributed triple hop adjustment strategy to address the topology
mismatch problem. The approach's ultimate goal is to shape the current overlay
graph $G$ into the \emph{Logical Communication Network (LCN)} $G^{*}$ which is
how the optimal overlay is referred in the paper's context. A formal
definition of achieving the above match is only if all peer hop sequences $(v_1,
v_2, \ldots, v_k)$ in $G$ exist in $G^{*}$ and in the same order\footnote{In
practice triple sequences $(v_1, v_2, v_3)$ are used.}. The mismatching
detection is done in the following way. Suppose we want to verify peer a
sequence, say $v_2-v_1-v_3$. A pair of probing messages are sent from $v_1$ to
$v_2$ and $v_3$. Suppose delays of $(v_1,v_2)$ and $(v_1,v_3)$ are denoted as
$x$ and $z$, respectively. When the probing message arrives to $v_2$ it forwards
it directly to $v_3$. Similarly, when the probing message arrives to $v_3$, it
forwards it directly to $v_2$. These last steps are performed in order to obtain
delays of $(v_2,v_3)$ and $(v_3,v_2)$ physical paths, respectively, denoted by
$y$. If $y=z-x\pm\varepsilon$, sequence $v_2-v_1-v_3$ is mismatched and should
be adjusted to $v_1-v_2-v_3$ by deleting edge $(v_1,v_3)$ and adding a new
$(v_2,v_3)$. If $y=x-z\pm\varepsilon$, sequence $v_2-v_1-v_3$ is mismatched and
should be adjusted to $v_1-v_3-v_2$ by deleting edge $(v_1,v_2)$ and adding a
new $(v_3,v_2)$, where $\varepsilon$ is a small positive real number denoting
additional delays caused by possible forwarding and jitter delays. The
advantages of the HAND algorithm compared to other approaches are that:
\begin{inparaenum}[\itshape i\upshape)]
  \item it does not need any clock synchronization,
  \item it is a fully distributed algorithm making it suitable for
        decentralized systems,
  \item the traffic overhead is low,
  \item it can be used in dynamic peer-to-peer environments, and
  \item maintains lower query response times.
\end{inparaenum}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Ono}
Choffnes and Bustamante propose Ono \cite{CB2008}, a protocol for managing
BitTorrent traffic so that it significantly reduces cross-ISP traffic and in the
same time enhances downloading rates by favoring connections within the borders
of a single autonomous system. Contrary to biased peer selection proposed in
\cite{BCCMSBZ2006}, this work can lead to improved performance without requiring
any cooperation between ISPs subscribers, or requiring any additional
infrastructure and network topology information. The selection approach is
landmark-based and leverages existing CDN infrastructure for peer distance
estimation. CDNs already use both static (i.e. geographical) and dynamic
(network measurement systems) information for their replica selection, so the
authors claim that peers which exhibit similar redirection behavior, are very
likely they are close to the replica servers and as a consequence to each other.
The redirection behavior is modeled in terms of \emph{ratio map} in the
article's parlance, a vector of <replica-server,ratio> tuples, where ratio is
the percentage of times CDN redirects the peer to the specific replica-server.
The bootstrapping phase consists of the peer performing DNS lookup to CDN names
in order to build its redirection information. The interval for polling DNSs
starts from 30 seconds and increases by one minute every time redirection
information to the CDN is found to remain unchanged after a lookup. On the other
hand, the interval is halved whenever is found to have been changed. In order
not to avoid the bootstrapping phase if the ratio map is sufficiently fresh, the
protocol persists the information after the end of a BitTorrent session.
